---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(GGally)
```

### Load data


```{r load-data}
setwd("E:/STUDY/DA/coursera/linear model")
load("movies.Rdata")
```



* * *

## Part 1: Data

We us str(movies) and head(movies) to get an idea of the dataset.
All data seem to be collected from the reliable source.

```{r}
str(movies)

```

* * *

## Part 2: Research question

I am very interested to know what are kinds of movies that are liked by both Audiance and Critics. This question interest me because there are many movies which are liked by audiance but are critically flooped and vice-versa. I want to find out whats in a movie that is liked by both of them. For this I will be using only Rotten tomato dataset as my response variable for two reasons a. Uniformity of Output.
        b. Seperation between audiance and critics rating is given only in Rotten tomatoes.

* * *

## Part 3: Exploratory data analysis

First of all let us analyze how audiance rating and critics rating are related to each othe using a scatter plot.

```{r}
plot(movies$audience_score,movies$critics_score,ylab="Critics Score",xlab="Audiance Score")
q<-lm(audience_score~critics_score,data=movies)
abline(q)

```

We can see that there is strong positive relationship. Thus audiance and critics score tend to increase with each other.We can see that variability is more in the middle than on sides which imply, average rated movies by audiance tend to be low to high rated by critics and vice-versa. Another thing we can notice is there are almost no films rated high by critics but low by audiance but there are few films which are rated high by audiance and low by critics. Thus films having high rating for critics tend to have high rating for audiance as well.  


Let us now create a new variable which is avrage of critics and average rating. This is the variable we tend to model.

```{r}
rating_avg <- (movies$critics_score + movies$audience_score)/2
hist(rating_avg)
```
Histogram gives an idea about output distribution.

Next we try to find correlation between similar looking input variables. We us GGally package for this.We will find correlation between all similar looking variables and plot their scatter

```{r}
 ggpairs(movies,7:12,title="Correlation table of dvd and theatre data")


```



* * *

## Part 4: Modeling

Step 1:

Let us first eliminate some variables from our common understanding. Variables that can be eliminated are title,thtr_rel_year,thtr_rel_month, thtr_rel_day,dvd_rel_year,dvd_rel_month,dvd_rel_day,imdb_url,rt_url. We create a new data set 'temp' after removing these variables.We also remove imdb ratings since a rating cant be used to predict another rating.

```{r}
temp <- movies[,c(3:6,19:30)]
str(temp)

```

We can further eliminate actor 1, actor2, actor 3, actor4 and actor 5,studio they seem to be less relevant and making our model very complex (since there are hundreds of leval of them).
Now we start creating our model with remaing data. We also need to add our newly created response variable 'rating_avg' in our data set.

```{r}
temp <- temp[,c(1:3,5:10)]
temp<- cbind(temp,rating_avg)
str(temp)

model1 <- lm(rating_avg~.,temp)
summary(model1)


```

Now we can start by applying the proccess of Backward elimination using p-values.
We remove best pic win,best actor win, best actress win from the model since it has the highest p value and make the new model.

```{r}
temp2 <- temp[,c(1:4,8,9,10)]
model2 <- lm(rating_avg~genre+runtime+mpaa_rating+best_pic_nom+best_dir_win+top200_box,temp2)
summary(model2)

```

Thus since all the p values are significant now, model2 is our final model.

which can be viewed using summary command (show above).


* * *

## Part 5: Prediction


We will make a prediction for a new movie 'Bridge of Spies' released in 2016.
Let us create a dataframe for all set of values of this movie and then use the predict command.


```{r}
ng <- data.frame(genre = "Drama",runtime = 135,mpaa_rating = "PG-13",best_pic_nom = "yes",best_dir_win = "no",top200_box="no")

predict(model2,ng)

```

Thus we can see that our model predict a rating (audiance+critics) of 79% for this movie which is quiet near to original rating.


* * *

## Part 6: Conclusion

Thus we can conclude that variables that make movies succesful between audiance and critics both are:
1. Genre (Animation, Musical & Performance arts, Documentry tend to be more succesful).
2. Runtime(Increase in runtime increase rating slightly).
3. Mpaa rating (PG 13 is worst for our purpose).
4. Whether nominated for best film.(This parameter is very imp. slope is 20, means nomination in best pictures increase rating by 20 points).
5. Whether won best director(This also increase rating if yes).
6. Part of top 200 boxoffice (Increase rating by 14 points if true).
